Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-25 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Results

When monitoring the experiments, using the graph database and the Cypher query language 
provided interesting views on the connected data difficult to replicate with a relational database. 
As an example we can consider comparing the difference between the number of volunteers in deployments
B and GG,(shown in figures \ref{fig:B-network} and \ref{fig:GG-network} respectivly) additional
metrics and patterns are available when they are treated as a network. The same can be applied to 
the population, or the interaction as a whole. For instance when creating a new individual 
parents could be selected if there is a minimum distance between them in the graph.

>>>>

When monitoring the experiments, using the graph database and the Cypher query language 
provided interesting views on the connected data difficult to replicate with a relational database. 
As an example we can consider comparing the difference between the number of volunteers in deployments
B and GG,(shown in figures \ref{fig:B-network} and \ref{fig:GG-network} respectivly) additional
metrics and patterns are available when they are treated as a network. The same can be applied to 
the population, or the interaction as a whole. The graph could be used also by the evolutionary
algorithm, for instance when creating a new individual 
parents could be selected only if there is a minimum distance between them in the graph.
